Python as a machine learning language: experiences from the \textit{scikit-learn} project

### 2013-06-09 paper.tex
KMeans example.

\textbf{Predictors.} The \textit{predictor} interface defines a \texttt{predict}
method taking as input some dataset \texttt{X} and producing as output
predictions for \texttt{X} based on the learned parameters of the estimator. In
the case of supervised learning estimators, this method typically returns the
predicted labels or values computed by the model. Some unsupervised learning
estimators may however also implement that interface: for example, in clustering
estimators, \texttt{predict} returns the identifiers of the closest clusters for
the samples in \texttt{X}.

@@

Continuing with the previous example, predictions on unseen data
\texttt{X\_test}, \texttt{y\_test} can therefore be obtained and evaluated using
the following snippet:
\begin{verbatim}
y_pred = clf.predict(X_test)
score = clf.score(X_test, y_test)
\end{verbatim}

>>>>

\textbf{Predictors.} The \textit{predictor} interface defines a \texttt{predict}
method taking as input some new data \texttt{X\_test} and producing as output
predictions for \texttt{X\_test} based on the learned parameters of the
estimator. In the case of supervised learning estimators, this method typically
returns the predicted labels or values computed by the model.  Continuing with
the previous example, predicted labels for \texttt{X\_test} can be obtained
using the following snippet:
\begin{verbatim}
y_pred = clf.predict(X_test)
\end{verbatim}
Some unsupervised learning
estimators may however also implement that interface, as illustrated below:
\begin{verbatim}
from sklearn.cluster import KMeans
km = KMeans(n_clusters=10)
km.fit(X_train)
clust_pred = km.predict(X_test)
\end{verbatim}
In the above example, a \texttt{KMeans} estimator is first fit on the training
data \texttt{X\_train}. Then the \texttt{predict} method is called on the test
data \texttt{X\_test} in order to retrieve predicted cluster labels.
The \texttt{predict} method in \textit{scikit-learn} thus offers a unified way
to compute predictions with respect to unseen data.

@@
